---
title: "Collaborative Fall 2020"
output: html_notebook
---

```{r include=FALSE}
library(dplyr)
library(tidyr)
```


# load survey results

```{r}
pre_collaborative_survey <- read.csv("data/survey result_collaborative Oct16.csv")
post_collaborative_survey <- read.csv("data/survey result_collaborative Dec18.csv")
```

# define item types

```{r}
positive_questions = c("question5","question6","question8","question11","question14","question15",
                       "question19","question21","question22","question24","question25","question27",
                       "question28")
negative_questions = c("question4","question7","question9","question12","question13","question16",
                       "question17","question18", "question20","question23","question26")

cost_questions = c("question4","question9","question10","question15","question16","question18",
                   "question23","question26")
benefit_questions = c("question5","question6","question7","question8","question9","question11",
                      "question12","question13","question14","question16","question17","question19",
                      "question20","question21","question22","question24","question25","question27",
                      "question28")
```

# First, we want to rescore the negative items

```{r}
# function for rescore negative items for collaborative survey
rescore_negative_collaborative <- function (collaborative_survey){
  negative <- collaborative_survey[ ,which((names(collaborative_survey) %in% negative_questions)==TRUE | names(collaborative_survey) == "Student")]
  
  not_negative <- collaborative_survey[ ,which((names(collaborative_survey) %in% negative_questions)==FALSE | names(collaborative_survey) == "Student")]
  
  negative[,-1] <- 6-negative[,-1]
  collaborative_survey <- merge(not_negative, negative,by="Student",all=T)
}

rescore_negative_collaborative(pre_collaborative_survey)
rescore_negative_collaborative(post_collaborative_survey)
```

```{r}
# create a new column grading students overall attitude
pre_collaborative_survey$totalscore <- rowSums(pre_collaborative_survey[,5:29])
post_collaborative_survey$totalscore <- rowSums(post_collaborative_survey[,5:29])

# get the mean of totalscore of students' attitude about collaboration
mean(pre_collaborative_survey$totalscore)
mean(post_collaborative_survey$totalscore)
```

# I cannot say the above improve is huge, let's look at individual questions


```{r}
# We calculate the difference of the mean of each question
individual_difference <- colMeans(post_collaborative_survey)-colMeans(pre_collaborative_survey)
individual_difference_rank <- arrange(as.data.frame(individual_difference),individual_difference)

individual_difference_rank
# most questions have little bit improves, if we could run it longer, we may have better outcomes
```


# I want to check the correlation between total score and past collaborative experience, not much find

```{r}
#(pre_collaborative_survey$totalscore,pre_collaborative_survey$question1)
#cor(pre_collaborative_survey$totalscore,pre_collaborative_survey$question2/3+pre_collaborative_survey$question3/5)
```

# check which types of items improved the most, cost items or benefit items

```{r}
pre_cost_items <- pre_collaborative_survey[ ,which((names(pre_collaborative_survey) %in% cost_questions)==TRUE)]
pre_benefit_items <- pre_collaborative_survey[ ,which((names(pre_collaborative_survey) %in% benefit_questions)==TRUE)]

post_cost_items <- post_collaborative_survey[ ,which((names(post_collaborative_survey) %in% cost_questions)==TRUE)]
post_benefit_items <- post_collaborative_survey[ ,which((names(post_collaborative_survey) %in% benefit_questions)==TRUE)]

pre_cost_items$totalscore <- rowSums(pre_cost_items)
pre_benefit_items$totalscore <- rowSums(pre_benefit_items)
post_cost_items$totalscore <- rowSums(post_cost_items)
post_benefit_items$totalscore <- rowSums(post_benefit_items)
mean(pre_cost_items$totalscore)/ncol(pre_cost_items)
mean(post_cost_items$totalscore)/ncol(post_cost_items)
mean(pre_benefit_items$totalscore)/ncol(pre_benefit_items)
mean(post_benefit_items$totalscore)/ncol(post_benefit_items)
```

# looks like they find collaborative not hard to do.


# load test results
```{r}
pre_test <- read.csv("data/pre-test Oct16.csv")
post_test <- read.csv("data/post-test Dec18.csv")

pre_test %>% group_by(version) %>% summarize(mean=mean(as.numeric(total),na.rm=T))
post_test %>% group_by(version) %>% summarize(mean=mean(as.numeric(total),na.rm=T))
```





